Selective electroporation of the viral envelope

### 2021-04-15 documents/pure_electroporation.tex
Whoops, wrong transfer function!

	\noindent As pulse duration is reduced from the microsecond to nanosecond regime, effects targeting smaller intracellular structures are expected and observed. Indeed, pulses shorter than 10 ns have been observed to porate the nuclear envelope and organelle membranes while leaving the plasma membrane intact. \\

>>>>

	\noindent As pulse duration is reduced from the microsecond to nanosecond regime, effects targeting smaller intracellular structures are expected and observed, and a degree of tunability arises. Indeed, pulses shorter than 10 ns have been observed to porate the nuclear envelope and organelle membranes while leaving the plasma membrane intact. \\
